\chapter{Searching for Drivers}
\label{searchForDrivers}

In this chapter we cover finding matching offers for a given request.
Searching for drivers is done when a requests gets newly created.
\index{Offer!finding matching offers for given request}
\index{Request!finding matching offers for given request}

\section{Step 1: Preselecting Offers}
Search DRPs for Offers, which conform to the following criteria:
\begin{enumerate}
\item{There exists a DRP for this offer,\\
       which has direct distance smaller than DRPs testradius to request's startpt \\
	\emph{AND} \\
	DRP has seatsAvaillable more or equal to the request required number of seats\\
	\emph{AND} \\
	DRP's expected arrival is within request's startTimeEarliest and startTimeLatest.
      }
\item{There exists a DRP for this offer, \\ 
       which has direct distance smaller than DRPs testradius to request's endpt\\
	\emph{AND} \\
	DRP has seatsAvaillable more or equal to the request required number of seats
	}
\end{enumerate}
Offers matching the above tests are added to a  \emph{preselection list}.
The follwing steps will be about subsequently removing false positives from the preselection list 
to finally obtain a set of exact matches in the end. 

\section{Step 2: Filtering by simple Criteria}
\label{sfdFilteringSimpleCriteria}
The preselection is filtered for simple criteria (smoker/gender/...etc).
Matches that do not match all of these conditions are removed from the preselection.
Note that this step does not require expensive calculation, so it should be performed before
calculating and checking the exact detour.

\section{Step 3: Calculating the Detour}
\label{sfdCalculatingDetour}
For each offer in the preselection list that passed the previous step, invoke the routing engine to calculate 
the corrected tour,  which includes the detour needed to pick up and drop the potential rider.
In this step all offers for which the detour is larger than the maximum detour defined by the driver
are removed from the preselection list. 	
      
\section{Step 4: Applying the Sorting Function}
\label{sfdSortingFunction}
Sort the remaining offers according to the scoring function.

\section{Step 5: Applying Limits}
\label{sfdApplyingLimits}
From the sorted list of requests, return the top $ml$ best scoring elements,
Where $ml$ is the riders individual "matchLimit", i.e the maximum number of 
matchings defined to be returned for the rider.
	
